### 2022-03-16 paper/localpsf.tex
restructuring paper

In this section we present three key concepts that our method is based on. The method itself will be presented in Section \ref{sec:method}. First, we define moments of the impulse responses $\phi_x$, and show how these moments can be computed efficiently (Section \ref{sec:intromoments}). Our method will use these moments extensively. Second, we describe an impulse response approximation that we call ``normalized local mean displacement invariance'' (Section \ref{sec:local_mean_displacement_invariance}). Our method will interpolate impulse responses using this approximation. Third, we discuss how discretization of continuous functions by finite elements leads to matrix discretizations $\mathbf{A}$ and $\mathbf{\Phi}$ of $\Aop$ and $\Phi$, respectively (Section \ref{sec:finite_element_kernel}). The goal of our method is to compute H-matrix approximations of these matrices. 
%While we use finite elements, other discretization schemes such as finite differences or finite volumes could be used instead with minor modifications.

@@

@@

The results from Section \ref{sec:intromoments} allow us to compute $V$, $\mu$, and $\Sigma$ by applying $\Aop^T$ to a small number of polynomial functions. Since a probability distribution concentrates within a small number of standard deviations of its mean, knowing $\mu(x)$ and $\Sigma(x)$ permits us to form an ellipsoid shaped estimate for the support of $\phi_x$, \emph{without} computing $\phi_x$ (Section \ref{eq:mean_and_covariance_estimation}). This allows us to compute large numbers of impulse responses, $\impulseresponse_{x_i}$, in ``batches,'' $\eta_b$ (see Figure \ref{fig:batches_intro}). We compute the impulse response batch $\eta_b$ by applying $\Aop$ to a weighted sum of point sources (Dirac comb) associated with a batch, $S_b$, of points $x_i$ scattered throughout $\Omega$ (Section \ref{sec:get_impulse_response}). The batch of points $S_b$ is chosen via a greedy ellipsoid packing algorithm so that, for $x_i,x_j \in S_b$, the support of $\impulseresponse_{x_i}$ and the support of $\impulseresponse_{x_j}$ do not overlap (or do not overlap much) if $i \neq j$ (Section \ref{sec:sample_point_selection}). Because these supports do not overlap, we can post-process $\eta_b$ to recover the functions $\impulseresponse_{x_i}$ associated with all points $x_i \in S_b$---with one application of $\Aop$, we recover many $\impulseresponse_{x_i}$ (Section \ref{sec:get_impulse_response}). The process is repeated to get more batches, until a desired number of impulse responses is reached.

@@

To determine $E_x$, we must compute the scalar $\spatialvol(x)$, the length-$\gdim$ vector $\spatialmean(x)$, and the $\gdim \times \gdim$ matrix $\spatialcov(x)$. In Section \ref{eq:mean_and_covariance_estimation} we will see that it is possible to compute $V(x)$, $\mu(x)$, and $\Sigma(x)$ for all $x \in \Omega$ simultaneously, via a procedure that involves applying $\Aop^T$ to a small number of polynomial functions (three functions if $\gdim=1$, six if $\gdim=2$, ten if $\gdim=3$).

>>>>

In this section we present the key concepts that our method is based on. The method itself will be presented in Section \ref{sec:method}. First, we define moments of the impulse responses, $\phi_x$, and show how these moments can be computed efficiently (Section \ref{sec:intromoments}). Our method will use these moments extensively. Second, we present ellipsoid shaped a-priori estimates for the supports of the impulse responses (Section \ref{eq:mean_and_covariance_estimation}). Our method will use these ellipsoid estimates to choose sets of impulse responses that can be computed in batches. Third, we describe an impulse response approximation that we call ``normalized local mean displacement invariance'' (Section \ref{sec:local_mean_displacement_invariance}). Our method will interpolate impulse responses using this approximation. Fourth, we discuss how discretization of continuous functions by finite elements leads to matrix discretizations $\mathbf{A}$ and $\mathbf{\Phi}$ of $\Aop$ and $\Phi$, respectively (Section \ref{sec:finite_element_kernel}). The primary function of our method is to compute H-matrix approximations of these matrices. 
%While we use finite elements, other discretization schemes such as finite differences or finite volumes could be used instead with minor modifications.

@@

%To determine $E_x$, we must compute the scalar $\spatialvol(x)$, the length-$\gdim$ vector $\spatialmean(x)$, and the $\gdim \times \gdim$ matrix $\spatialcov(x)$. In Section \ref{eq:mean_and_covariance_estimation} we will see that it is possible to compute $V(x)$, $\mu(x)$, and $\Sigma(x)$ for all $x \in \Omega$ simultaneously, via a procedure that involves applying $\Aop^T$ to a small number of polynomial functions (three functions if $\gdim=1$, six if $\gdim=2$, ten if $\gdim=3$).

@@

The results from Section \ref{sec:intromoments} allow us to compute $V$, $\mu$, and $\Sigma$ by applying $\Aop^T$ to a small number of polynomial functions, and the results of Section \ref{eq:mean_and_covariance_estimation} permit us to form an ellipsoid shaped estimate for the support of $\phi_x$, \emph{without} computing $\phi_x$. This allows us to compute large numbers of impulse responses, $\impulseresponse_{x_i}$, in ``batches,'' $\eta_b$ (see Figure \ref{fig:batches_intro}). We compute the impulse response batch $\eta_b$ by applying $\Aop$ to a weighted sum of point sources (Dirac comb) associated with a batch, $S_b$, of points $x_i$ scattered throughout $\Omega$ (Section \ref{sec:get_impulse_response}). The batch of points $S_b$ is chosen via a greedy ellipsoid packing algorithm so that, for $x_i,x_j \in S_b$, the support of $\impulseresponse_{x_i}$ and the support of $\impulseresponse_{x_j}$ do not overlap (or do not overlap much) if $i \neq j$ (Section \ref{sec:sample_point_selection}). Because these supports do not overlap, we can post-process $\eta_b$ to recover the functions $\impulseresponse_{x_i}$ associated with all points $x_i \in S_b$---with one application of $\Aop$, we recover many $\impulseresponse_{x_i}$ (Section \ref{sec:get_impulse_response}). The process is repeated to get more batches, until a desired number of impulse responses is reached.

@@
